---
title: "multiple linear regression"
author: "Rania Ahmed"
date: "September 5, 2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---
```{r muliple, echo=TRUE}
muliple <- read.csv(file.choose(), header= T)
attach(muliple)
View(muliple)
```

```{r, echo=TRUE}
library(dplyr)
newdata <- mutate(muliple, dummy_sex= ifelse(muliple$SEX=="Male", 1,0), dummy_outcome =ifelse(muliple$outcome=="Success", 1,0), dummy_treatment = ifelse(muliple$Treatment=="Newdrug", 1,0))  
View(newdata)
```


```{r, echo=TRUE}
corelations <- cor(newdata[ ,4:7])
library(corrplot)
corrplot(corelations, method = "circle")
corelations
```
#there is statistically significant only between outcome and treatment so the sex and hdl level don't affect the outcome
# the interpertation
```{r, echo=TRUE}
newdata <- within(newdata, Treatment <- relevel(Treatment, ref = "Placebo"))
logisticmodel <- glm(outcome~ Treatment+SEX+HDL_LEVEL, family = binomial, data = newdata)
summary(logisticmodel)
```

```{r, echo=TRUE}
library(Greg)
printCrudeAndAdjustedModel(logisticmodel)[-1,]
```
# First interpertation for cruded value which means the value of OR in the presence of other variables
1- the odds of success for patient recieving newdrug taking the considration the sex and HDL level is 10.09
2- the odds of success for a male patient who is recieving newdrug and has HDL level is 2.33
3- the odds of success for a patient in the presence of  HDL level taking the considration the sex and receiving new drug is 1.10
# second interpretation for Adjusted values which mean the value of OR of variables regardless the presences of other variables.
1- the odds of the success for the patient recieving new drug is 10.88
2- the odds of the success for a male patient is 2.46
3- the odds of success for a patient with HDL level is 1.07


